Paper_analyses

### 2022-02-03 Paper_Analyses_subj_obje_arousal.Rmd
timeseries bayes prevalence on pupil
added a way to visualise the bayesian prevalence on the timeseries of pupil data

table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$mediansplit_sample_arousal2))

mediansplit_sample_arousal2

table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$Group))

tmp.df4_full_stim_downs_jun2021_60bins %>%
  subset(Group == "NT")%>%
  # subset(!is.na(mediansplit_sample_arousal2))%>%
  ggplot(aes(x = timerezero3, y = pup_basCor))+
  stat_smooth(aes(group= mediansplit_sample_arousal2, color = mediansplit_sample_arousal2), fun = mean,geom = "line",
               se = F, alpha = .1, size = 1.5)+
  stat_smooth(aes(group=mediansplit_sample_arousal2, color = mediansplit_sample_arousal2), size = 3)+  
theme_classic()+
  ylab("Pupil size (z)")+
  xlab("Time (s)")+
  # p$graphstyle+
  scale_color_brewer(palette = "Dark2")+
  xlim(0,6)+
   facet_grid(~mediansplit_sample_valence2)

@@

# i =1
# unique(tmp.df4_full_stim_downs_jun2021_60bins$)
table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$arousal_c))
for (b in 1:length(nbins)) {
  # for (s in 1:length(nsim)) {

>>>>

@@

table(is.na(tmp.df4_full_stim_downs_jun2021_60bins$arousal_c))
for (b in 1:length(nbins)) {
  # for (s in 1:length(nsim)) {
